A Comparison of R Tools for Nonlinear Least Squares Modeling

### 2024-05-10 copyedit240208/2023-15-copyeditresponse.Rmd
uncommitted

```{r ex01, echo=TRUE}
weed <- c(5.308, 7.24, 9.638, 12.866, 17.069, 23.192, 31.443,
          38.558, 50.156, 62.948, 75.995, 91.972)
tt <- 1:12
weeddf <- data.frame(tt, weed)
plot(weeddf, main="Hobbs weed infestation data")
```

>>>>

```{r ex01, echo=TRUE, out.width="90%"}
weed <- c(5.308, 7.24, 9.638, 12.866, 17.069, 23.192, 31.443,
          38.558, 50.156, 62.948, 75.995, 91.972)
tt <- 1:12
weeddf <- data.frame(tt, weed)
plot(weeddf, main="Hobbs weed infestation data")
```
